---
title: "Dataprocessing_Statistic"
output: html_document
date: "2024-03-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir = "Workingdirectory")
library("tidyverse")
library("dplyr")
library("ggplot2")
library("writexl")
library("readxl")
library("psych")
```
##Function for Threshold
#Use the same for pitch and roll
```{r}
# Define a function to remove rows until the first occurrence of 0
Threshold_pitch <- function(file_path) {
  # Read the data from the specified TSV file
  sub_1TH <- read_tsv(file_path)
  
  # Split the data frame by the 'axis' column
  sub_1TH_split <- split.data.frame(sub_1TH, sub_1TH$axis)
  
  # Extract the 'pitch' data frame
  sub_1TH_pitch <- data.frame(sub_1TH_split$pitch)
  
  # Find the index of the first occurrence of 0 in the 'resp' column
  first_zero_index <- which(sub_1TH_pitch$resp == 0)[1]
  
  # Remove rows until the first zero
  sub_1TH_pitch <- sub_1TH_pitch[first_zero_index:nrow(sub_1TH_pitch), ]
  
  # Calculate the threshold as the mean of the remaining 'intensity' values
  Threshold <- mean(sub_1TH_pitch$intensity)
  assign("Threshold_pitch_sub", Threshold, envir = .GlobalEnv)
  
  # Return the modified data frame and the calculated threshold
  return(data_frame = sub_1TH_pitch)
}

.GlobalEnv$Threshold_pitch <- Threshold_pitch
```
## Data processing
For every participant separately!

#Position variabilty metrics (PVM) for 1 Participant

Hardwires
```{r}
Pitch1_csv = "Dataset1"
Pitch2_csv = "Dataset2"
Pitch3_csv = "Dataset3"

Roll1_csv = "Dataset4"
Roll2_csv = "Dataset5"
Roll3_csv = "Dataset6"

Threshold_sub = "Dataset_Threshold"
```

Load data
```{r}
#import pitch
Import_pitch_1 <- read.csv2(Pitch1_csv,header=FALSE, sep=",")
pitch_1 <- data.frame(Import_pitch_1$V6)
colnames(pitch_1)[1] <- "pitch1"

Import_pitch_2 <- read.csv2(Pitch2_csv,header=FALSE, sep=",")
pitch_2 <- data.frame(Import_pitch_2$V6) 
colnames(pitch_2)[1] <- "pitch1"

Import_pitch_3 <- read.csv2(Pitch3_csv,header=FALSE, sep=",")
pitch_3 <- data.frame(Import_pitch_3$V6)
colnames(pitch_3)[1] <- "pitch1"

pitch <- bind_rows(pitch_1,pitch_2,pitch_3)   #Bind Data in 1 column
pitch <- (pitch[-c(1:2),]) |> as.numeric() |>  #delete empty rows
  abs() #convert all numbers to positive numbers
pitch_degree <- as.matrix(pitch*(180/pi)) #convert to degree



#import roll

Import_roll_1 <- read.csv2(Roll1_csv, header=FALSE, sep=",")
roll_1 <- data.frame(Import_roll_1$V7)
colnames(roll_1)[1] <- "roll1"

Import_roll_2 <- read.csv2(Roll2_csv, header=FALSE, sep=",")
roll_2 <- data.frame(Import_roll_2$V7)
colnames(roll_2)[1] <- "roll1"

Import_roll_3 <- read.csv2(Roll3_csv, header=FALSE, sep=",")
roll_3 <- data.frame(Import_roll_3$V7)
colnames(roll_3)[1] <- "roll1"


roll <- bind_rows(roll_3,roll_2, roll_1)
roll<- (roll[-c(1:2),]) |> as.numeric() |>
  abs()

roll_degree <- as.matrix(roll*(180/pi))

```
#Threshold for 1 participant
```{r}
Threshold_pitch(Threshold_sub)
Threshold_roll(Threshold_sub)

Threshold_pitch_sub1 = Threshold_pitch_sub
Threshold_roll_sub1 = Threshold_roll_sub

```
Mean or SD
```{r}
#Mean Pitch

Sub_1_PVM_pitch <- mean(pitch_degree,na.rm = TRUE)

#Mean Roll

Sub_1_PVM_roll <-mean(roll_degree, na.rm = TRUE)



```

Write the Data to csv

```{r}
#Bind the data

sub1me <- data_frame(Sub_1_PVM_pitch, Sub_1_PVM_roll, Threshold_roll_sub1, Threshold_pitch_sub1)

#rename columne 
Names <- data_frame(
  "PVM_Pitch","PVM_Roll","Threshold_Pitch", "Threshold_roll"
)

sub1me <- rbind(names(Names), sub1me)

write.csv(sub1me, "sub1.csv")
```

##Bind the Data of every participant
```{r}
colnames(sub1me) <- colnames(sub2me)<- colnames(sub3me) <- colnames(sub4me) <- 
  colnames(sub5me) <- colnames(sub6me) <- colnames(sub7me)<- 
  colnames(sub8me)  <- colnames(sub9me) <- colnames(sub10me) <- 
  colnames(sub11me)<- colnames(sub12me) <- c("PVM.Pitch", "PVM.Roll", "Threshold.Roll", "Threshold.pitch")

rows <- lapply(list(sub1me, sub2me, sub3me,sub4me,sub5me,sub6me,sub7me,sub8me,sub9me,sub10me,sub11me,sub12me), function(df) df[2, ])
combined_matrix <- do.call(rbind, rows)

write.xlsx(combined_matrix, "DatenFA.xlsx")
```

##Statistics

Data import as log and without log

```{r}
DatenFA <- read_excel("DatenFA.xlsx")
DatenFA$PVM.Pitch <- as.numeric(DatenFA$PVM.Pitch)
DatenFA$PVM.Roll <- as.numeric(DatenFA$PVM.Roll)
DatenFA$Threshold.Roll <- as.numeric(DatenFA$Threshold.Roll)
DatenFA$Threshold.pitch <- as.numeric(DatenFA$Threshold.pitch)

DatenFA_log <- log(DatenFA)

```


Comparison Threshold and the PVM of "pitch" 

```{r}
linearRegression_pitch = lm(Threshold.pitch~PVM.Pitch, data =  DatenFA)
summary(linearRegression_pitch)

ggplot(linearRegression_pitch, aes(Threshold.pitch,PVM.Pitch)) + geom_point() + 
  geom_smooth(method = "lm")
```

Comparison Threshold and the PVM of "pitch" log

```{r}
linearRegression_pitchlog = lm(Threshold.pitch~PVM.Pitch, data =  DatenFA_log)
summary(linearRegression_pitchlog)
ggplot(linearRegression_pitchlog, aes(Threshold.pitch,PVM.Pitch)) + geom_point() + 
  geom_smooth(method = "lm")

```

Comparison Threshold and the PVM of "roll"

```{r}
linearRegression_roll = lm(Threshold.Roll~PVM.Roll, data = DatenFA)
summary(linearRegression_roll)
ggplot(linearRegression_roll, aes(Threshold.Roll,PVM.Roll)) + geom_point() + 
  geom_smooth(method = "lm")
```

Comparison Threshold and the PVM of "roll" log

```{r}
linearRegression_rolllog = lm(Threshold.Roll~PVM.Roll, data = DatenFA_log)
summary(linearRegression_rolllog)
ggplot(linearRegression_rolllog, aes(Threshold.Roll,PVM.Roll)) + geom_point() + 
  geom_smooth(method = "lm")
```

Comparison Threshold "pitch" and "roll"

```{r}
thp = DatenFA$Threshold.pitch
thr = DatenFA$Threshold.Roll
t.test(thp,thr, paired = TRUE)
anova(DatenFA)
```

